---
title: "Mini-project-1: A Hello World Function"
author: "Skye Zheng"
Date: "January 24, 2025"
fontsize: 12pt 
mainfont: "Times New Roman"
format: html
---

## Project description:

In this mini-project, a hello_world function is designed to greet people based on the time of day. 

## Code:
Install two packages first.

```{r,echo = TRUE, output = FALSE, warning=FALSE, message=FALSE}
#install.packages("stringr")
#install.packages("dplyr")

library(stringr)
library(dplyr)
```

Below is the main function of the hello_world. You can provide your name and the time of day to receive a greeting. Also, you can specify whether it is midnight right now, in which you will receive a surprise response. Optionally, you can choose to know how much time is left before your bedtime.

Inside the main function, there are three sub-functions: check_time, greeting_words, and time_left_for_bed. They are in a separate R script file.

```{r, hello_world_function, echo = TRUE, output = FALSE, warning=FALSE, message=FALSE}

# Inside Functions.R, there are three functions:
# check_time: categorizing the time into morning, afternoon, evening, and night.
# greeting_words: return greeting words based on the time of day.
# time_left_for_bed: tell people how much time is left until bedtime
source("Functions.R") 

# build a hello_world function: greeting each person 
hello_world <-function(name_list, time_of_day, is_midnight = FALSE, know_time_left = FALSE, bed_time = "22:00"){
  
  # name_list - a list of names
  # time_of_day - the time of day in string format "xx:xx"
  # is_midnight - a Boolean value to check if it is midnight
  # know_time_left - whether choose to know how much time left before bedtime
  # bed_time - the time to go to bed; bedtime can be customized if know_time_left == TRUE, default is "22:00".
  
  # Loop through each name in the name_list
  for (name in name_list){
    
    # Clean the name to standard format: capitalizing the first letter of each word and remove white spaces in the beginning and at the end
    name <- name %>%
      str_to_title() %>%
      str_trim()
    
    # 1. say hello to each name in the name_list
    print(paste("Hello", name, ">(^~^)<"))
    
    # 2. If they consider it is midnight currently, no further greetings, print "GO TO SLEEP RIGHT NOW!!!"
    if (is_midnight == TRUE){
      print(paste0("GO TO SLEEP RIGHT NOW!!! ", str_to_upper(name),"!"))
      next
    }
    
    # 3. If it is not midnight, print greeting words based on the time of day
    
    # Call check_time function to categorize the time into time period: morning/afternoon/evening/night
    time_period <- check_time(time_of_day) 
    
    # Call greeting_words function to randomly return greeting words based on the time period
    words <- greeting_words(time_period) 
    
    # Print Good morning/afternoon/evening/night and additional greeting words to the person!
    print(paste0("Good ", time_period,"! ", words))
    
    # 4. If know_time_left is TRUE, provide the time left before bedtime according to bed_time. 
    # Call time_left_for_bed function to get how many hours and minutes left before bedtime
    time_left <- time_left_for_bed(time_of_day, bed_time)
    if(know_time_left == TRUE){
      print(paste("You have", time_left[1], "hours and", time_left[2], "minutes left until bedtime."))
    } 
  }
}

```

## Now, it's time to test our functions!

**1. A person named Skye would like to know how much time is left until bedtime.**
```{r, test_1}
hello_world("Skye", "11:24", FALSE, TRUE)
```
**2. Greeting 3 people! They would also like to know how much time is left until bedtime.**
```{r, test_2}
hello_world(c("Skye","Jie","Feng"), "15:04", FALSE, TRUE, "23:00")
```

**3. Greeting Skye again! But this time, she does not want to know how much time is left until her bedtime ~**
```{r, test_3}
hello_world("skye", "21:50", FALSE)
```
**4. Greeting Skye and Christy! It is midnight!!**
```{r, test_4}
hello_world(c("Skye","Christy"), "23:34", TRUE)
```
**5. Greeting Skye and Christy again! Oops, they have white spaces in their names, but our `hello_world()` function removes those white spaces.**
```{r, test_5}
hello_world(c("  Skye  "," christy "), "23:34", TRUE)
```
## Thank you!

